%------------------------
% Resume Template
% Author : Pushp Vashisht
% Github : https://github.com/pushp1997/
% License : MIT
% Inspired By: https://github.com/arasgungore/arasgungore-CV
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE AASHNA}} & Email: \href{mailto:saashna@gmail.com}{saashna@gmail.com}~~~~~\\
  Mobile: \href{tel:+3530892117502}{(+353) 089-211-7502}~~~~~~~~~~~~~~~~ \\
  Github:~~ \href{https://github.com/aashna09}{github.com/aashna09} & LinkedIn: \href{https://www.linkedin.com/in/aashna-singh-a7148511a/}{linkedin.com/in/aashna-singh-a7148511a} \\
\end{tabular*}

%-----------SKILLS-----------------
\section{Skills Summary}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{~~~~~~Python, SQL, Shell Scripting}
\resumeSubItem{Tools}{~~~~~~~~~~~~~~Informatica Powercenter, SSIS, SSRS, MySQL, Oracle DB}
\resumeSubItem{Soft Skills}{~~~~~~~Leadership, Technical Writing, Adaptibility}
\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Accenture Pvt Ltd.}{Bangalore, India}
{Data Engineering Analyst}{May 2022 - July 2023}
\resumeItemListStart
\resumeItemWithoutTitle{Played a pivotal role as an ETL Informatica Developer for the esteemed client, Liberty Mutual.}
\resumeItemWithoutTitle{Extensively used Informatica ETL methodology for supporting Data extraction, Transformation and loading process, in a corporate-wide-ETL Solution using Informatica PowerCenter}
\resumeItemWithoutTitle{Achieved a significant reduction in ETL job runtime from 7-8 hours to 8 minutes through Unix script optimization and workflow tuning.}
\resumeItemWithoutTitle{Diligently addressed and resolved incidents by debugging mapping codes, ensuring smooth data flow and minimizing disruptions.}
\resumeItemWithoutTitle{Led the deployment process across various environments, starting from development, testing, staging, and culminating in production. Rigorously tested at each stage to ensure data integrity and system stability.}
\resumeItemWithoutTitle{Collaborated closely with the Database and DevOps teams to streamline deployments and enhance system performance.}
\resumeItem{Roles}{ETL Developer, 24X7 Production Support, Requirements Gathering.}
\resumeItem{Skills Acquired / Utilised}{Informatica Powercenter, SQL databses, ESP Scheduler, Unix, Agile Software Development.}
\resumeItemListEnd
\vspace{2pt}
\resumeSubheading
{Infosys Pvt Ltd.}{Bangalore, India}
{Senior Systems Engineer}{October 2019 - May 2022}
\resumeItemListStart
\resumeItemWithoutTitle{Developed bidirectional ECM to SF mappings using Informatica Intelligent Cloud Services.}
\resumeItemWithoutTitle{Addressed and resolved incidents efficiently by delving deep into mapping codes, ensuring continuous data flow and system reliability.}
\resumeItemWithoutTitle{Held full accountability for launching new Point Of Sale (POS) stores for Tiffany & Co., overseeing everything from database configurations to establishing end-to-end data pipelines, thereby ensuring smooth data integration across the newly inaugurated locations.}
\resumeItemWithoutTitle{Collaborated with cross-functional teams to ensure the successful launch and integration of new POS systems.}
\resumeItemWithoutTitle{Played a pivotal role in continuous enhancements and code migration.}
\resumeItem{Roles}{ETL Developer, Production Support Engineer, Jobs & Prodcution Monitoring.}
\resumeItem{Skills Acquired / Utilised}{Informatica Powercenter, Control-M, Unix, MySQL.}
\resumeItemListEnd
\vspace{2pt}
\resumeSubheading
{Infosys Limited}{Mysuru, India}
{Systems Engineer Trainee}{February 2019 - May 2019}
\resumeItemListStart
\resumeItemWithoutTitle{Completed an internship focused on Business Intelligence and Python programming.}
\resumeItemWithoutTitle{Developed a Taxi Booking System using SSIS and SSRS.}
\resumeItem{Roles}{Project Trainee, Backend Developer.}
\resumeItem{Skills Acquired / Utilised}{Python, SSIS, SSRS, Agile Software Development.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University College Cork}{Cork, Ireland}
{MSc - Computing Science}{2023 - Ongoing}
\vspace{2pt}
\resumeSubheading
{Maharishi Markandeshwar University}{Ambala, India}
{Bachelor of Technology - Computer Science \& Engineering;  GPA: 7.45}{2015 - 2019}
\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------VOLUNTEERING-----------------
\section{Volunteer Experience}
\resumeSubHeadingListStart
\resumeSubheading{Prayas Foundation}{Renukoot, India}
{Web Developer (Part-time)}{Aug 2019 - Apr 2020}
\resumeItemListStart
\resumeItemWithoutTitle{Developed the website (https://prayasfoundation.org.in), where the user can register to become a donor or request for blood. My work on this project involved designing and coding the website, as well as testing and debugging to ensure its
functionality.}
\resumeItemWithoutTitle{Volunteered at Lion's Club, organizing camps and supporting during Covid.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
